### 2022-08-18 ms/ms02_floats.tex
ENH suppl

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_2.png}
\end{subfigure}

\begin{subfigure}[]{.66\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_3.png}
\end{subfigure}
%
\caption{Gene ontology analysis of egenes of variants associated to two (\textbf{a}) and three (\textbf{b}) GWAS categories compared to egenes of variants associate to one GWAS category.} \label{fig:hist_gwas_egene_etissue}
\end{figure*}

>>>>

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_3.png}
\end{subfigure}

\begin{subfigure}[]{.66\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_2.png}
\end{subfigure}
%
\caption{Gene ontology analysis of egenes of variants associated to three (\textbf{a}) and two (\textbf{b}) GWAS categories compared to egenes of variants associated to one GWAS category.} \label{fig:gene_ontology}
\end{figure*}
